Realizing Temporal Graphs

### 2023-01-24 RealizingTemporalGraphs.tex
Work from Tuesday 24th of January

    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
    We start by fixing a label of one arbitrary edge as $a$, where $a \in [\Delta]$.
    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
    Note, w.l.o.g we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling. Therefore, all together the whole algorithm is performed in polynomial time.
\end{proof}

@@

\begin{proof}
As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
Note, w.l.o.g we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
\end{proof}

@@

@@

For an easier understanding and the analysis of the algorithm we give the following definition.
\begin{definition}
    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
    A path $P = (u=v_1,v_2, \dots, v_p = v)$ in $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
    is called a \emph{segment}. Denote it with $S_{u,v}$.
\end{definition}
From the definition it follows, that there are $O(k^2)$ segments in $G'$.
Observe also that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.

@@

For every edge $e$ in $G'$ that is incident to a vertex of interest we create a variable $x_e$ that can have values from $ \{1, 2, \dots, \Delta\}$.
Each vertex of interest is incident to at most $k$ such edges, therefore we create $O(k^3)$ variables.

@@

In the case when we want to guess the fastest path from $u$ to $v$, that passes through the vertex $x$ we write it as a fastest path of form $u \rightarrow x \rightarrow v$.

@@

    This gives us $O(k^{k^5})$ guesses.

@@

    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$, 
    where the first one includes $v_2, v_{p-1} \in U^*$, 
    and the second one includes $z_2, z_{p-1} \in U^*$.

@@

    $v_2 \rightarrow u \rightarrow w \rightarrow z_2$,
    $v_2 \rightarrow u \rightarrow z \rightarrow z_2$,
    $v_2 \rightarrow u \rightarrow w \rightarrow z_{r-1}$ and
    $v_2 \rightarrow u \rightarrow z \rightarrow z_{r-1}$.
    We repeat this procedure for all pairs of segments and all vertices from $U^*$ in those segments.
    Since there are $O(k^3)$ segments in $G'$,
    there are $O(k^6)$ possible paths of this form.
    \item For a segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$

@@

    $w \rightarrow u \rightarrow v_2$, $w \rightarrow v \rightarrow v_2$,

@@

    $v_2 \rightarrow u \rightarrow w$, $v_2 \rightarrow v \rightarrow w$.

@@

    For a fixed segment $S_{u,v}$ and a fixed vertex of interest $w$ we have $O(4 k^k)$ different possible such paths, therefore we make $O(k^6)$ guesses for these paths.
    All together we made $O(k^6)$ new guesses for the structure of all of the above mentioned fastest temporal paths.

@@

    In fact, this is true for all paths starting in any vertex not in $S_{w,z}$.

@@

    $S_{w,z}$ have to increase up to the certain point, when traversing the segment coming through $w$ and coming through $z$.
    Namely,
    let $z_j \in S_{w,z} \setminus \{w,z\}$ be the vertex with the biggest value  $D_{v_i,z_j}$,
    we call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
    Then $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 

@@

    or determine that this kind of vertex does not exist.

@@

    which results in producing $O(k^6)$ new guesses.
    \item At the end we also guess the permutation of all $O(k^3)$ variables, \ie for any two variables $x_e$ and $x_f$, we know if $x_e < x_f$ or $x_e = x_f$, or $x_e > x_f$.
    This results in $O(k^k)$ guesses.

@@

We create all of the guesses iteratively.

@@

\begin{claim}\label{claim:FPT-uv-LabelAlmostalledges}
    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
    is a $u,v$ path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = | v_i \in \{P \setminus \{u,v \} \} \cap U |$.
    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, up to the constant $c_{uv} = \lambda(uv_2)$,
    such that the labeling $\lambda$ respects $D'$.
    Moreover, for the labels of edges that cannot be determined precisely, we can get some extra restrictions.
\end{claim}

@@

\begin{claim}\label{claim:FPT-unlabeldPaths-01}
    Suppose that
    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
    Suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
    travels through the same two vertices $u$ and $w$.
    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or $z,v$.
\end{claim}
\begin{proof}
    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
    Denote with $P_{v_i,z_j}^\ell$
    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
    Let us observe the following possibilities.
    \\
    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
    Denote this path as $P^1_{v_i,z_\ell}$.
    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
    \\
    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
    Denote this path as $P^2_{v_i,z_\ell}$.
    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_ell$.
    Therefore since
    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
    and since there is unique way to
    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
    \\
    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
    Denote this path as $P^3_{v_i,z_\ell}$.
    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
\end{proof}

\subsection{Adding constraints to the ILP}
We proceed with adding constraints to our ILP instance, by iterating through all pairs of vertices.
We now describe how we add constraints to a path. Whenever we say that a duration of a path gives an equality or inequality constraint, we mean the following.
Let $P=(u=v_1,v_2, \dots, v_p = v)$ be the underlying path of a fastest temporal path from $u$ to $v$,
and let $Q = (u=z_1,z_2, \dots, z_r = v)$ be the underlying path of another temporal path from $u$ to $v$.
Then we know that $d(P,\lambda) = D_{u,v}$ and $d(Q, \lambda) \geq D_{u,v}$.
Using \cref{obs:durationPwithWaitingTimes}
we create an \emph{equality constraint} for $P$
of the form 
\begin{equation}\label{eq:FPT-equalityConstraint}
    D_{u,v} = \sum _ {i=2} ^ {p-1} (\lambda (v_{i}v_{i+1}) - \lambda (v_{i-1}v_i))_\Delta + 1,
\end{equation}
and an \emph{inequality constraint} for $Q$ 
\begin{equation}\label{eq:FPT-inequalityConstraint}
    D_{u,v} \leq \sum _ {i=2} ^ {r-1} (\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))_\Delta + 1.
\end{equation}
In both cases we implicitly assume that if the difference of $(\lambda (z_{i}z_{i+1}) - \lambda (z_{i-1}z_i))$ is smaller than zero, for some $i$, we add the value $\Delta$ to it (\ie we consider the difference modulo $\Delta$), therefore we have the sign $\Delta$ around the brackets.
In \emph{TODO: claim ???}\todo{TBD} we prove that for any two consecutive edges we know if the difference of labels is positive or negative, therefore we know when $\Delta$ has to be added.

First case we observe is the case when we want to determine the labels on fastest temporal paths among vertices of interest.
We proceed in the following way.
Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
If $P_{u,v}$ is a segment we determine all the labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-Labelalledges}).
%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
In the case when $P{_u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-LabelAlmostalledges}).
In both cases we introduce the equality constraint for $P_{u,v}$ (as in \cref{eq:FPT-equalityConstraint}).
%Since there are $\ell - 1$ edge labels that are not determined with respect to the label of the first edge, may be some  TODO from above??

After finishing the previous step for all pairs of vertices in $U$,
the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path.
Let us call these edges \emph{determined edges}, and the edges that were not determined with the respect to some other edge label up to now the \emph{undetermined} edges.
If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a variable $x_e$.
Note that the undetermined edges are exactly the ones that are not a part of any fastest temporal path.
Let us first observe some properties of such edges.

>>>>

    Now, given the matrix of travel delays $T$, we can find a labeling $\lambda$ that satisfies $D$.
    We start by fixing a label of one arbitrary edge as $a$, where $a \in [\Delta]$.
    Knowing the label of one edge, and all waiting times in $T$, we can uniquely determine the labels of all other edges.
    More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
    the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
    Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
    Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
    It is not hard to see, that also the calculation of the labeling $\lambda$ takes polynomial time, as we have to traverse the graph exactly once, to successfully fix the labeling. Therefore, all together the whole algorithm is performed in polynomial time.
\end{proof}

@@

\begin{proof}
As stated above, we can determine travel delays at every vertex in $O(n^2)$ time. 
Once all of the delays are calculated, we have to only construct the labeling $\lambda$ that satisfies the matrix $D$. 
We start by fixing a label of one edge as $a$, where $a \in [\Delta]$.
Knowing the label of edge $v_1v_2$ and all waiting times in $T$, we can uniquely determine the labels of all other edges.
More specifically, if we know that $\lambda(v_i v_j) = a$, then for all $v_k \in N(v_i)$ (resp.~$v_{k'} \in N(v_j)$)
the value $\lambda(v_iv_k) \equiv a + \tau_{v_i}^{v_j,v_k} \pmod \Delta $ (resp.~$\lambda(v_j v_{k'}) \equiv a + \tau_{v_j}^{v_i,v_{k'}} \pmod \Delta $).
Since there are $\Delta$ options to fix the first label, we can find $\Delta$ different labelings satisfying $D$.
Note, w.l.o.g. we can start determining the labeling $\lambda$ by setting $\lambda(v_1v_2) = 1$.
\end{proof}

@@

\section{W[1]-hardness}
\begin{theorem}\label{thm:W1wrtFVS}
    \deltaExactLong\ is W[1]-hard parameterized by the feedback vertex number.
\end{theorem}
\begin{proof}
    We present a parameterized reduction from the W[1]-hard problem \textsc{Multicolored Clique} parameterized by the number of colors~\cite{fellows2009multipleinterval}.  Here, given a $k$-partite graph $H=(W_1\uplus W_2 \uplus\ldots\uplus W_k, F)$, we are asked whether $H$ contains a clique of size $k$. If $w\in W_i$, then we say that $w$ has \emph{color} $i$. W.l.o.g.\ we assume that $|W_1|=|W_2|=\ldots=|W_k|=n$ and that every vertex has at least one neighbor of every color. 
    Furthermore, for all $i\in[k]$, we assume the vertices in $W_i$ are ordered in some arbitrary but fixed way, that is, $W_i=\{w^i_1,w^i_2,\ldots,w^i_n\}$.
    Let $F_{i,j}$ with $i<j$ denote the set of all edges between vertices from $W_i$ and $W_j$. We assume w.l.o.g.\ that $|F_{i,j}|=m$ for all $i< j$.
    Furthermore, for all $i<j$ we assume that the edges in $F_{i,j}$ are ordered in some arbitrary but fixed way.

    Given an instance $H$ of \textsc{Multicolored Clique}, we construct an instance $D$ of \deltaExactLong\ as follows. To ease the presentation, we first describe the underlying graph $G$ that is implicitly defined by the entries $D_{v,v'}=1$, that is, the pairs of vertices $v,v'$ that should be connected by a temporal path of duration one, meaning that there needs to an edge connecting the two vertices. Afterwards, we describe the remaining entries of $D$.

    We use the following subgraph $G_{i,j}$ as a \emph{edge selection gadget} for color combination $i,j$ with $i<j$. We first describe the vertex set of $G_{i,j}$.
    \begin{itemize}
        \item A set $X_{i,j}$ of vertices $x_1, x_2, \ldots, x_m$.
        \item A set $Y_{i,j}$ of vertices $y_1, y_2, \ldots, y_m$.
        \item A set $Z_{i,j}$ of vertices $z_1, z_2, \ldots, z_m$.
        \item Vertex sets $U_1, U_2, \ldots, U_m$ with $U_\ell=\{u^\ell_1, u^\ell_2,\ldots, u^\ell_n, u^\ell_{n+1}, u^\ell_{n+2}, u^v_{2n}\}$ for all $\ell\in[m]$. Let $U_{i,j}=\bigcup_{\ell\in[n]} U_\ell$.
        \item Two special vertices $v_{i,j}^\star,v_{i,j}^{\star\star}$.
    \end{itemize}
    Graph $G_{i,j}$ has the following edges.
    \begin{itemize}
        \item For all $\ell\in [m]$ we have edge $\{x_\ell,v_{i,j}^\star\}$, $\{y_\ell,v_{i,j}^\star\}$, and $\{z_\ell,v_{i,j}^{\star\star}\}$.

        Furthermore, we have edges $\{y_\ell,u^\ell_1\}$ and $\{z_\ell,u^\ell_{2n}\}$.
        \item For all $\ell\in [m]$ and $\ell'\in [2n-1]$, we have edge $\{u^\ell_{\ell'},u^\ell_{\ell'+1}\}$.
    \end{itemize}
    This finishes the construction of the edge selection gadget $G_{i,j}$.

    For each color $i$, we introduce the following vertices. Intuitively, what we describe in the following will be used as a \emph{verification gadget} for color $i$.
    \begin{itemize}
        \item We have $k-1$ vertices $v^i_\ell$ for $\ell\in[k]\setminus\{i\}$ and one vertex $v^i$.
        \item If $1\neq i\neq k$, then we have a set $\hat{U}_i$ of $n$ additional vertices $\hat{u}^i_1,\hat{u}^i_2,\ldots,\hat{u}^i_n$.
    \end{itemize}
    We add the following edges. Assume $1\neq i \neq k$. We describe the two cases $i=1$ and $i=k$ afterwards. Let $e_\ell\in F_{1,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v^i,u^\ell_{\ell'}\}$ between $v^i$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget $G_{1,i}$.

    Let $1<j<i$ and let $e_\ell\in F_{j,i}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v_{j-1}^i,u^\ell_{\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{\ell'}$ of the edge selection gadget $G_{j,i}$.
    Furthermore, we add edge $\{v_{j}^i,u^\ell_{\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{\ell'+1}$ of the edge selection gadget $G_{j,i}$.

    We add edge $\{v^i_{i-1},\hat{u}^i_1\}$ and for all $\ell\in[n-1]$ we add edge $\{\hat{u}^i_\ell,\hat{u}^i_{\ell+1}\}$.

    Let $e_\ell\in F_{i,i+1}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{\hat{u}^i_n,u^\ell_{n+\ell'}\}$ between $\hat{u}^i_n$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget $G_{i,i+1}$.

    Let $i<j\le k$ and let $e_\ell\in F_{i,j}$ let $w^i_{\ell'}\in W_i$ be incident with $e_\ell$. Then we add edge $\{v_{j-1}^i,u^\ell_{n+\ell'}\}$ between $v^i_{j-1}$ and the vertex $u^\ell_{n+\ell'}$ of the edge selection gadget $G_{i,j}$.
    Furthermore, we add edge $\{v_{j}^i,u^\ell_{n+\ell'+1}\}$ between $v^i_j$ and the vertex $u^\ell_{n+\ell'+1}$ of the edge selection gadget $G_{i,j}$.

    Finally, we add two vertices $\hat{v},\hat{v}'$ and the following edges. Intuitively, what we describe next will be used to connect many vertex pairs by short paths, which will make arguing about possible labelings in yes-instances much easier.
    \begin{itemize}
        \item Edge $\{\hat{v},\hat{v}'\}$.
        \item An edge between $\hat{v}$ an all vertices in $X_{i,j}\cup Y_{i,j} \cup Z_{i,j}\cup U_{i,j}$ for all $1\le i<j\le k$.
        \item An edge between $\hat{v}'$ an all vertices in $X_{i,j}\cup Y_{i,j} \cup Z_{i,j}\cup U_{i,j}$ for all $1\le i<j\le k$.
    \end{itemize}
\end{proof}

@@

For an easier understanding and the analysis of the algorithm we give the following definition.
\begin{definition}
    Let $U \subseteq V(G')$ be a set of vertices of interest and let $u,v \in U$.
    A path $P = (u=v_1,v_2, \dots, v_p = v)$  in graph $G'$, where all inner vertices are not in $U$, \ie $v_i \notin U$ for $i \in \{ 2, 3, \dots, p-1\}$,
    is called a \emph{segment} from $u$ to $v$. We denote it as $S_{u,v}$.
    Note $S_{u,v} \neq S_{v,u}$.
\end{definition}
From the definition it follows, that there are $O(k^2)$ segments in $G'$.
Observe also that a temporal path in $G'$ between two vertices of interest is either a segment, or consists of a sequence of some segments.
%For a pair $u,v$ of vertices in $U$, there are $O(k!)=O(k^k)$ possible paths in $G'$ between them.

@@

@@

In the case when we want to guess the fastest path from $u$, that (somehow) passes through the vertex $x$, and goes directly to $v$ via an edge, we write it as a fastest path of form $u \leadsto x \rightarrow v$.
Similarly it holds if we want to include more vertices, that has to be visited by the path. If there is an edge (\ie a unique path) among two vertices, we denote it by $\rightarrow$,
if the path among two vertices is not uniquely determined, we denote it by $\leadsto$.

@@

    This gives us $O(k^{k^4})$ guesses.

@@

    first one between vertices $u,v \in U$, second one between vertices $w, z \in U$.

@@

    $v_2 \rightarrow u \leadsto w \rightarrow z_2$,
    $v_2 \rightarrow u \leadsto z \rightarrow z_2$,
    $v_2 \rightarrow u \leadsto w \rightarrow z_{r-1}$ and
    $v_2 \rightarrow u \leadsto z \rightarrow z_{r-1}$.
    We repeat this procedure for all pairs of segments.
    Since there are $O(k^2)$ segments in $G'$,
    there are $O(k^{k^5})$ possible paths of this form.
    \item \label{FPT:guess-uToSegment}
    For a segment $S_{u,v} = (u=v_1,v_2, \dots, v_p = v)$

@@

    $w \leadsto u \rightarrow v_2$, $w \leadsto v \rightarrow v_2$,

@@

    $v_2 \rightarrow u \leadsto w$, $v_2 \rightarrow v \leadsto w$.

@@

    For a fixed segment $S_{u,v}$ and a fixed vertex of interest $w$ we have $O(k^k)$ different possible such paths, therefore we make $O(k^{k^4})$ guesses for these paths.
    %All together we made $O(k^{k^4}$  new guesses for the structure of all of the above mentioned fastest temporal paths.

@@

@@

    $S_{w,z}$ have to increase up to a certain point, when traversing the segment coming through $w$ and coming through $z$.
    We split the analysis into two cases.
        \item 
    There is a single vertex $z_j \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
    More specifically, $z_j \in S_{w,z} \setminus \{w,z\}$ is the vertex with the biggest value  $D_{v_i,z_j}$.
    We call this vertex a \emph{split vertex of $v_i$ in the segment $S_{wz}$}.
    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j}$ and 

@@

    or determine that $z_j$ does not exist.

@@

    which results in producing $O(k^{k^6})$ new guesses.
    Note, $v_i \in S_{u,v}$ is fixed when calculating the split vertex for all other segments $S_{w,z}$.
    \item 
    There are two vertices $z_j, z_{j+1} \in S_{w,z}$ for which the duration from $v_i$ is the biggest.
    More specifically, $z_j, z_{j+1} \in S_{w,z} \setminus \{w,z\}$ are the vertices with the biggest value  $D_{v_i,z_j} = D_{v_i,z_{j+1}}$.
    Then it holds that $D_{v_i,z_2} < D_{v_i,z_3} < \dots < D_{v_i,z_j} = D_{v_i,z_{j+1}} > D_{v_i,z_{j + 2}} > \cdots > D_{v_i,z_{p-1}}$ and 
    From this it follows that the fastest temporal paths from $v_i$ to $z_2, z_3, \dots, z_{j}$ go through $w$,
    In this case we only need to guess the following two fastest temporal paths $u \leadsto w \rightarrow z_2$
    and $u \leadsto z \rightarrow z_{p-1}$.
    Each of this paths we then uniquely extend along the segment $S_{w,z}$ up to the vertex $v_j$, resp.~$v_{j+1}$,
    which give us fastest temporal paths from $u$ to $v_j$ and from $u$ to $v_{j+1}$.
    Note that in this case we do not introduce any new guesses, as we guessed these paths already in Step~\ref{FPT:guess-uToSegment}.

@@

We create all of the guesses independently.

@@

\begin{claim}\label{claim:FPT-uv-LabelAlmostalledges}
    Let $u, v \in U$ be two arbitrary vertices of interest and suppose that $P = (u=v_1, v_2, \dots, v_p = v)$, where $p \geq 2$, 
    is a $u,v$ path in $G'$, which is also the underlying path of a fastest temporal path from $u$ to $v$.
    Let $\ell_{u,v} \geq 1$ be the number of vertices of interest in $P$ different to $u,v$, namely $\ell_{u,v} = | v_i \in \{P \setminus \{u,v \} \} \cap U |$.
    We can determine the labeling $\lambda$ of all but $\ell_{u,v}$ edges of $P$, with respect to the label $\lambda(uv_2)$ of the first edge,
    such that the labeling $\lambda$ respects the values from $D$.
    Moreover, for the labels of edges that cannot be determined precisely, we can get some extra restrictions.
\end{claim}

@@

\begin{claim}\label{claim:FPT-unlabeldPaths-01}
    Suppose that
    $S_{u,v}, S_{w,z}$ are two segments with $ v_i \in S_{u,v}$ and $z_j \in S_{w,z}$,
    where $z_j$ is a split vertex of $v_i$ in the segment $S_{w,z}$.
    W.l.o.g. suppose that the fastest temporal path from $v_i$ to $z_j$ travels through vertices $u$ and $w$.
    Then the fastest temporal path from $v_i$ to any other vertex of $S_{w,z}$, that is closer to $w$,
    travels through the same two vertices $u$ and $w$.
    Similarly it holds for the cases when the fastest temporal path travels through $w,v$ or $z,u$ or $z,v$.
\end{claim}
\begin{proof}
    Let $z_\ell$ be a vertex of $S_{w,z}$, that is closer to $w$ than $z$ in the segment.
    Let us denote with $P_{v_i,z_j}$ the underlying path of the fastest temporal path from $v_i$ to $z_j$.
    Denote with $P_{v_i,z_j}^\ell$
    the subpath of the fastest temporal path from $v_i$ to $z_j$, that terminates in $z_\ell$.
    We want to show that $P_{v_i,z_j}^\ell$ is an underlying path of a fastest temporal path from $v_i$ to $z_j$.
    Let us observe the following possibilities.
    \\
    First, suppose for the contradiction, that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $u$ and $z$.
    Denote this path as $P^1_{v_i,z_\ell}$.
    Then it follows that $d(P^1_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$, which would imply that
    the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^1_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
    \\
    Second, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $w$.
    Denote this path as $P^2_{v_i,z_\ell}$.
    Note that $P_{v_i,z_j}^\ell$ and $P^2_{v_i,z_\ell}$ intersect on a segment $S_{w,z}$ from the vertex $w$ to $z_\ell$.
    Therefore since
    $d(P^2_{v_i,z_\ell}, \lambda) \leq d(P_{v_i,z_j}^\ell,\lambda)$,
    and since there is unique way to
    extend the path $P^2_{v_i,z_\ell}$ from $z_\ell$ to $z_j$, denote the extended path as $P^j_{v_i,z_\ell}$,
    we get that $d(P^j_{v_i,z_\ell}, \lambda) \leq $$(P_{v_i,z_j},\lambda)$.
    Which implies that $d(P^j_{v_i,z_\ell}, \lambda) = d(P_{v_i,z_j}, \lambda)$.
    Now using the similar argument it follows that $d(P_{v_i,z_j}^\ell, \lambda) = d(P^2_{v_i,z_\ell}, \lambda)$,
    therefore $P_{v_i,z_j}^\ell$ is also a fastest temporal path from $v_i$ to $z_j$.
    \\
    Third, suppose that the fastest temporal path from $v_i$ to $z_\ell$ travels through vertices $v$ and $z$.
    Denote this path as $P^3_{v_i,z_\ell}$.
    Then the duration of the temporal path from $v_i$ to $z_j$ using the subpath of $P^3_{v_i,z_\ell}$, would be strictly smaller than the duration of $(P_{v_i,z_j},\lambda)$, which cannot be possible.
\end{proof}

\subsection{Adding constraints and variables to the ILP}
First case we observe is the case when we want to determine the labels on fastest temporal paths among vertices of interest.
We proceed in the following way.
Let $u,v \in U$ be two vertices of interest and let $P_{u,v}$ be the fastest temporal path from $u$ to $v$.
If $P_{u,v}$ is a segment we determine all the labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-Labelalledges}).
%Note that since we determined labels of all edges, with respect to the first edge, we also know the exact values of waiting times at each inner vertex of $P_{u,v}$, when traversing the path.
In the case when $P{_u,v}$ is a sequence of $\ell$ segments, we determine all but $\ell - 1$ labels of edges of $P$, with respect to the label of the first edge (see \cref{claim:FPT-uv-LabelAlmostalledges}).
%In both cases we introduce the equality constraint for $P_{u,v}$ (as in \cref{eq:FPT-equalityConstraint}).
%Since there are $\ell - 1$ edge labels that are not determined with respect to the label of the first edge, may be some  TODO from above??

After finishing the previous step for all pairs of vertices in $U$,
the edges of fastest temporal paths from $u$ to $v$, where $u,v \in U$, are determined with respect to the label of the first edge of each path.
Let us call these edges \emph{determined edges}, and the edges that were not determined with the respect to some other edge label up to now the \emph{undetermined} edges.
If the fastest temporal path among two vertices $u,v \in U$ is just an edge $e$, then we treat it as being determined, since it gets assigned a label $\lambda(e)$ with respect to itself.
Note that the undetermined edges are exactly the ones that are not a part of any fastest temporal path.
Let us first observe some properties of such edges.
